Paper 2: Vitamin D

### 2018-04-24 doc/vitaminD.Rmd
changed plot format to document style

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot_slides("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  # dplyr::filter(acrStatus != "Normoalbuminuria") %>% 
  scatter_plot_slides("log(VitaminD)", "log(udbpCr)", 
               "log serum 25(OH)D (nmol/L)",
               "log uVDBP:cr (μg/mmol)")

>>>>

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  # dplyr::filter(acrStatus != "Normoalbuminuria") %>% 
  scatter_plot("log(udbpCr)", "log(VitaminD)", 
                "log uVDBP:cr (μg/mmol)",
               "log serum 25(OH)D (nmol/L)")
